Yaourt pliss\'{e}, yaourt flamb\'{e}

### 2014-01-29 plis_figures.tex
Reorganise fig:thickness in line + graph + x800. Markers to indicate respective thicknesses

\usepackage{siunitx}
\usepackage{multirow}

@@

\begin{figure}
	\begin{tikzpicture}
	\begin{axis}[%
		name=g,
		width=\columnwidth,
		height=0.4\columnwidth,
		xmin=0,xmax=1,xlabel={gap (\si{\milli\metre})},
		xtick={0.1,0.3,...,0.9},
		ymin=0,ylabel={$\lambda$ (\si{\milli\metre})},
		]
		\addplot+[only marks,Accent1, mark options={fill=Accent1}] coordinates {(0.05,0.261) (0.1,0.458) (0.250,0.916) (0.450,2.075) (0.800,3.333)};
		\addplot+[domain=0:3, no marks, Accent1, forget plot] {4.23*x};
	\end{axis}

	\matrix[matrix of nodes, inner sep=0, matrix anchor=south west, column sep=0.033\columnwidth, row sep=0.5em] at ($(g.outer north west)+(0,0.5em)$) (m) {
		\SI{50}{\micro\metre} & \SI{100}{\micro\metre}\\
		\includegraphics[width=0.225\columnwidth]{pattern_50um.jpg} &
		\includegraphics[width=0.225\columnwidth]{pattern_100um.jpg}\\
		\SI{250}{\micro\metre} & \SI{450}{\micro\metre}\\
		\includegraphics[width=0.225\columnwidth]{pattern_250um.jpg} &
		\includegraphics[width=0.225\columnwidth]{pattern_450um.jpg}\\
	};
	\node[inner sep=0, below left] at ($(m-2-1.north west) + (\columnwidth,0)$) (x800) {\includegraphics[width=0.45\columnwidth]{pattern_800um_x1.jpg}};
	\node[anchor=base] at (x800.north |- m-1-2.base) {\SI{800}{\micro\metre}};
	\draw[ultra thick, Accent2, <->] (x800.south west) ++(0.18\columnwidth, 0.05\columnwidth) -- ++(0.133\columnwidth,0) node[midway,above]{$\lambda$};
	\draw[ultra thick](x800.south east) ++(0,-0.5em) -- ++(-0.2\columnwidth,0) node[midway, below] {\SI{5}{\milli\metre}};
	\end{tikzpicture}
	\caption{Cell thickness dependence of the patterns. Scale bar is common for all 5 transmission microscopy pictures.}
	\label{fig:thickness}
\end{figure}

>>>>

\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{multirow}

@@

\begin{figure}
	\begin{tikzpicture}
	\matrix[matrix of nodes, inner sep=0, column sep=0.01\columnwidth, row sep=0.01\columnwidth] (m) {
		\includegraphics[width=0.245\columnwidth]{pattern_50um.jpg}&
		\includegraphics[width=0.245\columnwidth]{pattern_100um.jpg}&
		\includegraphics[width=0.245\columnwidth]{pattern_250um.jpg}&
		\includegraphics[width=0.245\columnwidth]{pattern_450um.jpg}\\
	};
	\node[inner sep=0, below left=0.01\columnwidth and 0 of m.south east] (x800) {\includegraphics[width=0.49\columnwidth]{pattern_800um_x1.jpg}};
	\draw[ultra thick, Accent2, <->] (x800.south west) ++(0.196\columnwidth, 0.05\columnwidth) -- ++(0.145\columnwidth,0) node[midway,above]{$\lambda$};
	\draw[ultra thick,Main](x800.north east) -- ++(-0.217\columnwidth,0) node[midway,below] {\SI{5}{\milli\metre}};

	\begin{axis}[%
		name=g,
		anchor=left of north west,
		at={($(m.south west)+(0,-0.01\columnwidth)$)},
		scale only axis,
		width=0.4\columnwidth,
		height=0.175\columnwidth,
		xmin=0,xmax=1,xlabel={gap (\si{\milli\metre})},
		xtick={0,0.4,...,0.9},
		ymin=0,ylabel={$\lambda$ (\si{\milli\metre})},
		label shift=-0.5em,
		cycle multi list={%
			Accent1,no marks\\%
			Accent1,only marks,every mark/.append style={fill=Accent1},mark=*\\%
			Accent1,only marks,every mark/.append style={fill=white},mark=*\\%
			Accent1,only marks,every mark/.append style={fill=Accent1},mark=triangle*\\%
			Accent1,only marks,every mark/.append style={fill=white},mark=triangle*\\%
			Accent1,only marks,every mark/.append style={fill=Accent1},mark=square*\\%
			Accent1,only marks,every mark/.append style={fill=white},mark=square*\\%
		}
		]
		\addplot+[domain=0:3] {4.23*x};
		\addplot coordinates {(0.05,0.261)};\label{pgfplots:50}
		\addplot coordinates {(0.1,0.458)};\label{pgfplots:100}
		\addplot coordinates {(0.250,0.916)};\label{pgfplots:250}
		\addplot coordinates {(0.450,2.075)};\label{pgfplots:450}
		\addplot coordinates {(0.800,3.333)};\label{pgfplots:800}
		%\addplot+[only marks,Accent1, mark options={fill=Accent1}] coordinates {(0.05,0.261) (0.1,0.458) (0.250,0.916) (0.450,2.075) (0.800,3.333)};
	\end{axis}
	\node[below right=0 of m-1-1.north west] {\ref{pgfplots:50}};
	\node[below right=0 of m-1-2.north west] {\ref{pgfplots:100}};
	\node[below right=0 of m-1-3.north west] {\ref{pgfplots:250}};
	\node[below right=0 of m-1-4.north west] {\ref{pgfplots:450}};
	\node[below right=0 of x800.north west] {\ref{pgfplots:800}};
	\end{tikzpicture}
	\caption{Cell thickness dependence of the patterns. Each transmission microscopy picture corresponds to a point on the graph. Scale bar is common for all pictures.}
	\label{fig:thickness}
\end{figure}
